---
title: "Fitting_GEVDistn"
author: "Sarah Jordan"
date: "5/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ismev)
source("utils.R")
library(ggplot2)
library(fitdistrplus)
library(extRemes)
setwd('C:\\Users\\smjor\\OneDrive - University of Virginia\\Class\\CE5500\\Final\\Code')
```

## Read in Data 

```{r cars}
GFDL_maxQ = read.csv('../Data/GFDL_maxQ.csv')
CCSM_maxQ = read.csv('../Data/CCSM_maxQ.csv')
```

## Fit Models

### Stationary

```{r pressure, echo=FALSE}
GFDL_stat = gev.fit(GFDL_maxQ$Uncontrolled)
CCSM_stat = gev.fit(CCSM_maxQ$Uncontrolled)
gev.diag(GFDL_stat)
gev.diag(CCSM_stat)
```

The fits on the stationary models actually look decent, but now let's explore non-stationary parameters to see how the model improves or not. 


#### Non-Stationary

##### GFDL

First, look at location (mul parameter in gev.fit). 

Resource to guide on non-stationary distributions:
http://www.mas.ncl.ac.uk/~nlf8/teaching/mas8391/background/chapter5.pdf

```{r}
# create time feature that will be a proxy of how the parameters are changing over time.
ti = matrix(ncol=1, nrow=length(GFDL_maxQ$Year))
ti[,1] = seq(1,length(GFDL_maxQ$Year),1)

# set mul to 1 to have non-stationary location parameter 
GFDL_mu = gev.fit(GFDL_maxQ$Uncontrolled, ti, mul=1)

# print deviance statistic, which has a chi-quared distn
D = 2*(-1* GFDL_mu$nllh - (-1*GFDL_stat$nllh))
print(D)
```
The asymptotic distribution of D is given by a Chi-squared distribution with k degrees of freedom, where k is the difference in dimensionality between the two models. With a deviance statistic of 0.05, this is small compared to a $\chi^2_1(0.05) = 3.841$, so we don't like this model. (https://web.ma.utexas.edu/users/davis/375/popecol/tables/chisq.html)

Now look at scale parameter only: 

```{r}
GFDL_sigl = gev.fit(GFDL_maxQ$Uncontrolled, ti, sigl=1)
D = 2*(-1* GFDL_sigl$nllh - (-1*GFDL_stat$nllh))
print(D)
```

This is sigificant, so scale is non-stationary. Now look at shape:
```{r}
GFDL_shl = gev.fit(GFDL_maxQ$Uncontrolled, ti, shl=1)
D = 2*(-1* GFDL_shl$nllh - (-1*GFDL_stat$nllh))
print(D)
```
Not significant. 

Now look at combinations of each, starting with location and scale:

```{r}
GFDL_mu_sigl = gev.fit(GFDL_maxQ$Uncontrolled, ti, mul=1, sigl=1)
D = 2*(-1* GFDL_mu_sigl$nllh - (-1*GFDL_stat$nllh))
print(D)
```

How does this compare to scale alone?

```{r}
D = 2*(-1* GFDL_mu_sigl$nllh - (-1*GFDL_sigl$nllh))
print(D) 
```
Here we added 1 degree of freedom, so it's still above that 3.84 threshold. 

Now let's look at shape, scale, and location all together:

```{r}
GFDL_mu_sigl_shl = gev.fit(GFDL_maxQ$Uncontrolled, ti, mul=1, sigl=1, shl =1)
D = 2*(-1* GFDL_mu_sigl_shl$nllh - (-1*GFDL_stat$nllh))
print(D)
```

Non-stationary scale and location parameters are best for GFDL. Now lets' go through the same process for CCSM projection.

##### GFDL
```{r}
print("------loc--------------")
CCSM_mu = gev.fit(CCSM_maxQ$Uncontrolled, ti, mul=1)
D = 2*(-1* CCSM_mu$nllh - (-1*CCSM_stat$nllh))
print(D)
print("------loc,scale------------")
CCSM_mu_sigl = gev.fit(CCSM_maxQ$Uncontrolled, ti, mul=1, sigl=1)
D = 2*(-1* CCSM_mu_sigl$nllh - (-1*CCSM_stat$nllh))
print(D)

print("------all3------------")
CCSM_mu_sigl_shl = gev.fit(CCSM_maxQ$Uncontrolled, ti, mul=1, sigl=1, shl=1)
D = 2*(-1* CCSM_mu_sigl_shl$nllh - (-1*CCSM_stat$nllh))
print(D)
```
Same result. Best model for CCSM is also non-stationary with mu and sigma as a function of time. 



### Fit all Models

We will assume this distribution for all reservoir operations as well; a more thorough study could take care to fit each individually to its non-stationary parameters. But we will assume location adn scale are non-stationary for all options.
```{r}
GFDL = list()
CCSM = list()
Objectives = list("Hydropower", "Environment", "Recession", "Cotton", "Sugar","Uncontrolled")
for(o in Objectives){
    print(o)
    a = gev.fit(as.numeric(unlist(GFDL_maxQ[o])), ti, mul=1, sigl=1)
    GFDL[[o]] = a$mle 
    b = gev.fit(as.numeric(unlist(CCSM_maxQ[o])), ti, mul=1, sigl=1)
    CCSM[[o]] = b$mle 

} 
```







### Calculate mu and sigma over time

```{r}
GFDL_mus = list()
CCSM_mus = list()

for(o in Objectives){
    i = seq(1989, 2099, 1)
    mus = lapply(i, function(x) GFDL[[o]][1] + GFDL[[o]][2]*(x - 1988))
    GFDL_mus[[o]] = mus
    mus = lapply(i, function(x) CCSM[[o]][1] + CCSM[[o]][2]*(x - 1989 + 1))
    CCSM_mus[[o]] = mus
}


GFDL_sigs = list()
CCSM_sigs = list()
for(o in Objectives){
    i = seq(1989, 2099, 1)
    sigs = lapply(i, function(x) GFDL[[o]][3] + GFDL[[o]][4]*(x - 1988))
    GFDL_sigs[[o]] = sigs
    sigs = lapply(i, function(x) CCSM[[o]][3] + CCSM[[o]][4]*(x - 1989 + 1))
    CCSM_sigs[[o]] = sigs
}
```

```{r}
ggplot() + 
    # geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Hydropower)), color="Hydropower")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Hydropower)), color="Hydropower")) + 
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Environment)), color="Environment")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Environment)), color="Environment")) + 
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Recession)), color="Recession")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Recession)), color="Recession")) + 
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Sugar)), color="Sugar")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Sugar)), color="Sugar")) + 
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Cotton)), color="Cotton")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Cotton)), color="Cotton")) + 
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Uncontrolled)), color="Uncontrolled")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Uncontrolled)), color="Uncontrolled")) + 
scale_color_manual(values = c("Hydropower" = "grey", 
                             "Environment" = "green", 
                             "Recession" = "blue", 
                             "Sugar" = "purple", 
                             "Cotton" = "orange",
                             "Uncontrolled" = "black"))+ 
labs(color='Legend') +
ylab("Mu") +
xlab("Year") + 
    ylim(1000,4000) + 
    ggtitle("GFDL-ESM2G.rcp26")

ggsave('../Figures/MuPlot_GFDL.png')
```
```{r}
ggplot() + 
    geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Hydropower)), color="Hydropower")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Hydropower)), color="Hydropower")) + 
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Environment)), color="Environment")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Environment)), color="Environment")) + 
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Recession)), color="Recession")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Recession)), color="Recession")) + 
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Sugar)), color="Sugar")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Sugar)), color="Sugar")) + 
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Cotton)), color="Cotton")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Cotton)), color="Cotton")) + 
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_mus$Uncontrolled)), color="Uncontrolled")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_mus$Uncontrolled)), color="Uncontrolled")) + 
scale_color_manual(values = c("Hydropower" = "grey", 
                             "Environment" = "green", 
                             "Recession" = "blue", 
                             "Sugar" = "purple", 
                             "Cotton" = "orange",
                             "Uncontrolled" = "black"))+ 
labs(color='Legend') +
ylab("Mu") +
xlab("Year") + 
    ylim(1000,4000) + 
    ggtitle("CCSM4.rcp85")

ggsave('../Figures/MuPlot_CCSM.png')
```

```{r}
ggplot() + 
    geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Hydropower)), color="Hydropower")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Hydropower)), color="Hydropower"),lty="dashed") + 
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Environment)), color="Environment")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Environment)), color="Environment"),lty="dashed") + 
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Recession)), color="Recession")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Recession)), color="Recession"),lty="dashed") + 
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Sugar)), color="Sugar")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Sugar)), color="Sugar"), lty="dashed") + 
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Cotton)), color="Cotton")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Cotton)), color="Cotton"), lty="dashed") + 
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Uncontrolled)), color="Uncontrolled")) +
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Uncontrolled)), color="Uncontrolled"), lty="dashed") + 
scale_color_manual(values = c("Hydropower" = "grey", 
                             "Environment" = "green", 
                             "Recession" = "blue", 
                             "Sugar" = "purple", 
                             "Cotton" = "orange",
                             "Uncontrolled" = "black"))+ 
labs(color='Legend') +
ylab("Sigma") +
xlab("Year") +
    ylim(0,2100) + 
    ggtitle("CCSM4.rcp85")

ggsave('../Figures/SigmaPlot_CCSM.png')
```
```{r}
ggplot() + 
    #geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Hydropower)), color="Hydropower")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Hydropower)), color="Hydropower")) + 
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Environment)), color="Environment")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Environment)), color="Environment")) + 
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Recession)), color="Recession")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Recession)), color="Recession")) + 
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Sugar)), color="Sugar")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Sugar)), color="Sugar")) + 
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Cotton)), color="Cotton")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Cotton)), color="Cotton")) + 
#geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(CCSM_sigs$Uncontrolled)), color="Uncontrolled")) +
geom_line(aes(x=c(seq(1989, 2099)), y =as.numeric(unlist(GFDL_sigs$Uncontrolled)), color="Uncontrolled")) + 
scale_color_manual(values = c("Hydropower" = "grey", 
                             "Environment" = "green", 
                             "Recession" = "blue", 
                             "Sugar" = "purple", 
                             "Cotton" = "orange",
                             "Uncontrolled" = "black"))+ 
labs(color='Legend') +
ylab("Sigma") +
xlab("Year") +
    ylim(0,2100) + 
    ggtitle("GFDL-ESM2G.rcp26")

ggsave('../Figures/SigmaPlot_GFDL.png')
```

### Return Periods
```{r}
GFDL_returnPeriods = list()
CCSM_returnPeriods = list()


calcReturns = function(shape, scale, location){
    q.100 = qgev(1-1/100, 
                shape =shape,
                scale =scale,
                location=location)
    q.500 = qgev(1-1/500, 
            shape =shape,
            scale =scale,
            location=location)
    return(list("q100"=q.100, "q500"=q.500))
}


hydro.df = data.frame(matrix(ncol=5, nrow=0))
env.df = data.frame(matrix(ncol=5, nrow=0))
rec.df = data.frame(matrix(ncol=5, nrow=0))
sug.df = data.frame(matrix(ncol=5, nrow=0))
cot.df = data.frame(matrix(ncol=5, nrow=0))
uc.df = data.frame(matrix(ncol=5, nrow=0))

# colnames(hydro.df) =c("Year", "GFDL.q100", "GFDL.q500", "CCSM.q100", "CCSM.q500")


returnPeriods = c("Hydropower" = hydro.df, "Environment" = env.df, "Recession" = rec.df, "Sugar" = sug.df, "Cotton" = cot.df, "Uncontrolled" = uc.df)

years = seq(1989, 2099,1)

createDataFrame = function(o, df,years){
    for(y in years){
        shape = GFDL[[o]][5]
        scale = as.numeric(unlist(GFDL_sigs[[o]][y - 1988]))
        loc = as.numeric(unlist(GFDL_mus[[o]][y - 1988]))
        GFDLvalues = calcReturns(shape, scale, loc)
        shape = CCSM[[o]][5]
        scale = as.numeric(unlist(CCSM_sigs[[o]][y - 1988]))
        loc = as.numeric(unlist(CCSM_mus[[o]][y - 1988]))
        CCSMvalues = calcReturns(shape, scale, loc)

        values = c(y, GFDLvalues$q100, GFDLvalues$q500, CCSMvalues$q100, CCSMvalues$q500)
        df = rbind(df, values)
        
}
    colnames(df) = c("Year", "GFDL.q100", "GFDL.q500", "CCSM.q100", "CCSM.q500")
    return(df)
}



```





```{r}
hydro.df  = createDataFrame('Hydropower', hydro.df,years)
env.df = createDataFrame('Environment', env.df,years)
rec.df = createDataFrame('Recession', rec.df,years)
sug.df = createDataFrame('Sugar', sug.df,years)
cot.df = createDataFrame('Cotton', cot.df,years)
uc.df = createDataFrame('Uncontrolled', uc.df,years)
```


Confidence intervals 

```{r}
set.seed(1)

hydro.df.CI = data.frame(matrix(ncol=4, nrow=0))
env.df.CI = data.frame(matrix(ncol=4, nrow=0))
rec.df.CI = data.frame(matrix(ncol=4, nrow=0))
sug.df.CI = data.frame(matrix(ncol=4, nrow=0))
cot.df.CI = data.frame(matrix(ncol=4, nrow=0))
uc.df.CI = data.frame(matrix(ncol=4, nrow=0))

# colnames(hydro.df) =c("Year", "GFDL.q100", "GFDL.q500", "CCSM.q100", "CCSM.q500")



years = seq(1989, 2099,1)

createDataFrame = function(o, df,years){
    for(y in years){
        shape = GFDL[[o]][5]
        scale = as.numeric(unlist(GFDL_sigs[[o]][y - 1988]))
        loc = as.numeric(unlist(GFDL_mus[[o]][y - 1988]))
        
        
        shape = CCSM[[o]][5]
        scale = as.numeric(unlist(CCSM_sigs[[o]][y - 1988]))
        loc = as.numeric(unlist(CCSM_mus[[o]][y - 1988]))
        CCSMvalues = calcReturns(shape, scale, loc)

        values = c(y, GFDLvalues$q100, GFDLvalues$q500, CCSMvalues$q100, CCSMvalues$q500)
        df = rbind(df, values)
        
}
    colnames(df) = c("Year", "GFDL.q100", "GFDL.q500", "CCSM.q100", "CCSM.q500")
    return(df)
}


```



### What if we assumed a stationary distribution with all of this data?
```{r}
GFDL_params = list()
CCSM_params = list()

for(o in Objectives){
    GFDL_params[[o]] = gevMOM(as.numeric(unlist(GFDL_maxQ[o])))
    CCSM_params[[o]] = gevMOM(as.numeric(unlist(CCSM_maxQ[o])))

}

GFDL_MLE = list()
CCSM_MLE = list()

for(o in Objectives){
    print(o)
    print("GFDL")
    GFDL_MLE[[o]] = fitdist(GFDL_maxQ[[o]], "gev", 
                           start=list(shape=GFDL_params[[o]]$kappa,
                                     scale = GFDL_params[[o]]$alpha,
                                     location = GFDL_params[[o]]$xi),
                           method="mle")
    plot(GFDL_MLE[[o]])
    print("CCSM")
    CCSM_MLE[[o]] = fitdist(as.numeric(unlist(CCSM_maxQ[[o]])), "gev", 
                       start=list(shape=CCSM_params[[o]]$kappa,
                                 scale = CCSM_params[[o]]$alpha,
                                 location = CCSM_params[[o]]$xi),
                       method="mle")
    plot(CCSM_MLE[[o]])

}
```

```{r}
hydro.df.stationary = data.frame(matrix(ncol=5, nrow=0))
env.df.stationary = data.frame(matrix(ncol=5, nrow=0))
rec.df.stationary = data.frame(matrix(ncol=5, nrow=0))
sug.df.stationary = data.frame(matrix(ncol=5, nrow=0))
cot.df.stationary = data.frame(matrix(ncol=5, nrow=0))
uc.df.stationary = data.frame(matrix(ncol=5, nrow=0))


createDataFrameStationary = function(o, df, GFDL_MLE, CCSM_MLE){
    y = o
    shape = GFDL_MLE[[o]]$estimate[1]
    scale = GFDL_MLE[[o]]$estimate[2]
    loc = GFDL_MLE[[o]]$estimate[3]
    GFDLvalues = calcReturns(shape, scale, loc)
    
    # bootstrap the data and re-estimate parameters
    gev.boot = bootdist(GFDL_MLE[[o]], bootmethod="nonparam")

    # compute the 100 and 500-yr floods of each bootstrapped fit
    m = gev.boot$nbboot # number of bootstrap replicates
    q100s.gev = sapply(1:m, function(i) try(qgev(1-1/100, 
                                                gev.boot$estim[i,1], 
                                                gev.boot$estim[i,2], 
                                                gev.boot$estim[1,3]), 
                                          TRUE))
    q500s.gev = sapply(1:m, function(i) try(qgev(1-1/500, 
                                                gev.boot$estim[i,1], 
                                                gev.boot$estim[i,2],
                                                gev.boot$estim[i,3]), 
                                        TRUE))

    # sort all the 100 and 500-yr floods from lowest to highest
    q100s.gev = sort(as.numeric(q100s.gev))
    q500s.gev = sort(as.numeric(q500s.gev))
    q100s.gev = head(q100s.gev, -1)
    q500s.gev = head(q500s.gev, -1)
    
    # compute a 90% confidence interval on the 100 and 500-yr flood estimates
    m = length(q100s.gev)
    GFDL_q100_CI.gev = c(q100s.gev[as.integer(0.05*m)], q100s.gev[as.integer(0.95*m)])
    GFDL_q500_CI.gev = c(q500s.gev[as.integer(0.05*m)], q500s.gev[as.integer(0.95*m)])

    
    shape = CCSM_MLE[[o]]$estimate[1]
    scale = CCSM_MLE[[o]]$estimate[2]
    loc = CCSM_MLE[[o]]$estimate[3]
    CCSMvalues = calcReturns(shape, scale, loc)
    
    
    # bootstrap the data and re-estimate parameters
    gev.boot = bootdist(CCSM_MLE[[o]], bootmethod="nonparam")

    # compute the 100 and 500-yr floods of each bootstrapped fit
    m = gev.boot$nbboot # number of bootstrap replicates
    q100s.gev = sapply(1:m, function(i) try(qgev(1-1/100, 
                                                gev.boot$estim[i,1], 
                                                gev.boot$estim[i,2],
                                                gev.boot$estim[i,3]), 
                                          TRUE))
    q500s.gev = sapply(1:m, function(i) try(qgev(1-1/500, 
                                                gev.boot$estim[i,1], 
                                                gev.boot$estim[i,2],
                                                gev.boot$estim[i,3]), 
                                        TRUE))

    # sort all the 100 and 500-yr floods from lowest to highest
    q100s.gev = sort(as.numeric(q100s.gev))
    q500s.gev = sort(as.numeric(q500s.gev))

    # compute a 90% confidence interval on the 100 and 500-yr flood estimates
    m = length(q100s.gev)
    CCSM_q100_CI.gev = c(q100s.gev[as.integer(0.05*m)], q100s.gev[as.integer(0.95*m)])
    CCSM_q500_CI.gev = c(q500s.gev[as.integer(0.05*m)], q500s.gev[as.integer(0.95*m)])
    
    print(GFDL_q100_CI.gev)
    print(GFDL_q500_CI.gev)
    print(CCSM_q100_CI.gev)
    print(CCSM_q500_CI.gev)
    values = c("Obj"=y, "GFDL.q100"=GFDLvalues$q100, "GFDL.q100.90LB" = GFDL_q100_CI.gev[1], "GFDL.q100.90UB"=GFDL_q100_CI.gev[2], "GFDL.q500"= GFDLvalues$q500, "GFDL.q500.90LB" = GFDL_q500_CI.gev[1], "GFDL.q500.90UB"=GFDL_q500_CI.gev[2], "CCSM.q100"=CCSMvalues$q100, "CCSM.q100.90LB" = CCSM_q100_CI.gev[1], "CCSM.q100.90UB"=CCSM_q100_CI.gev[2],"CCSM.q500"=CCSMvalues$q500,"CCSM.q500.90LB" = CCSM_q500_CI.gev[1], "CCSM.q500.90UB"=CCSM_q500_CI.gev[2])
    
    return(values)
}


hydro.df.stationary  = createDataFrameStationary('Hydropower', hydro.df.stationary)
env.df.stationary = createDataFrameStationary('Environment', env.df.stationary)
rec.df.stationary = createDataFrameStationary('Recession', rec.df.stationary)
sug.df.stationary = createDataFrameStationary('Sugar', sug.df.stationary)
cot.df.stationary = createDataFrameStationary('Cotton', cot.df.stationary)
uc.df.stationary = createDataFrameStationary('Uncontrolled', uc.df.stationary)


```

```{r}
write.csv(hydro.df.stationary, '../Data/StatCI_Hyd.csv')
write.csv(env.df.stationary, '../Data/StatCI_Env.csv')
write.csv(rec.df.stationary, '../Data/StatCI_Rec.csv')
write.csv(sug.df.stationary, '../Data/StatCI_Sug.csv')
write.csv(cot.df.stationary, '../Data/StatCI_Cot.csv')
write.csv(uc.df.stationary, '../Data/StatCI_Unc.csv')


```

```{r}
write.csv(hydro.df, '../Data/ReturnPeriods_Hyd.csv')
write.csv(env.df, '../Data/ReturnPeriods_Env.csv')
write.csv(rec.df, '../Data/ReturnPeriods_Rec.csv')
write.csv(sug.df, '../Data/ReturnPeriods_Sug.csv')
write.csv(cot.df, '../Data/ReturnPeriods_Cot.csv')
write.csv(uc.df, '../Data/ReturnPeriods_Unc.csv')
```


#### Now what if we only looked at historical data?
```{r}
set.seed(15)
GFDL_hist = GFDL_maxQ[which(GFDL_maxQ$Year < 2019),]
CCSM_hist = CCSM_maxQ[which(CCSM_maxQ$Year < 2019),]

GFDL_params = list()
CCSM_params = list()

for(o in Objectives){
    GFDL_params[[o]] = gevMOM(as.numeric(unlist(GFDL_hist[o])))
    CCSM_params[[o]] = gevMOM(as.numeric(unlist(CCSM_hist[o])))

}

GFDL_MLE = list()
CCSM_MLE = list()

for(o in Objectives){
    print(o)
    print("GFDL")
    GFDL_MLE[[o]] = fitdist(GFDL_hist[[o]], "gev", 
                            order=c(1,2,3), memp=memp.centered,

                           start=list(shape=GFDL_params[[o]]$kappa,
                                     scale = GFDL_params[[o]]$alpha,
                                     location = GFDL_params[[o]]$xi),
                           method="mme")
    plot(GFDL_MLE[[o]])
    print("CCSM")
    CCSM_MLE[[o]] = fitdist(as.numeric(unlist(CCSM_hist[[o]])), "gev", 
                      order=c(1,2,3), memp=memp.centered,

                       start=list(shape=CCSM_params[[o]]$kappa,
                                 scale = CCSM_params[[o]]$alpha,
                                 location = CCSM_params[[o]]$xi),
                       method="mme")
    plot(CCSM_MLE[[o]])

}

hydro.df.stationary.hist = data.frame(matrix(ncol=5, nrow=0))
env.df.stationary.hist = data.frame(matrix(ncol=5, nrow=0))
rec.df.stationary.hist = data.frame(matrix(ncol=5, nrow=0))
sug.df.stationary.hist = data.frame(matrix(ncol=5, nrow=0))
cot.df.stationary.hist = data.frame(matrix(ncol=5, nrow=0))
uc.df.stationary.hist = data.frame(matrix(ncol=5, nrow=0))

hydro.df.stationary.hist  = createDataFrameStationary('Hydropower', hydro.df.stationary.hist, GFDL_MLE, CCSM_MLE)
env.df.stationary.hist = createDataFrameStationary('Environment', env.df.stationary.hist, GFDL_MLE, CCSM_MLE)
rec.df.stationary.hist = createDataFrameStationary('Recession', rec.df.stationary.hist,GFDL_MLE, CCSM_MLE)
sug.df.stationary.hist = createDataFrameStationary('Sugar', sug.df.stationary.hist,GFDL_MLE, CCSM_MLE)
cot.df.stationary.hist = createDataFrameStationary('Cotton', cot.df.stationary.hist,GFDL_MLE, CCSM_MLE)
uc.df.stationary.hist = createDataFrameStationary('Uncontrolled', uc.df.stationary.hist,GFDL_MLE, CCSM_MLE)

```
```{r}
write.csv(hydro.df.stationary.hist, '../Data/HistStatCIMLE_Hyd.csv')
write.csv(env.df.stationary.hist, '../Data/HistStatCIMLE_Env.csv')
write.csv(rec.df.stationary.hist, '../Data/HistStatCIMLE_Rec.csv')
write.csv(cot.df.stationary.hist, '../Data/HistStatCIMLE_Cot.csv')
write.csv(sug.df.stationary.hist, '../Data/HistStatCIMLE_Sug.csv')
write.csv(uc.df.stationary.hist, '../Data/HistStatCIMLE_Unc.csv')
```

